### 2016-02-20 introduction.tex
abstract intro changes

Recent advances in automated test generation, reported in numerous papers and implemented in powerful tools \cite{csmith,jsfunfuzz,ISSTA12,LangFuzz,ZhendongPLDI,ZhendongOOPSLA}, have made it easier to find subtle faults in compilers.  Unfortunately, the blessing of many failing test cases can quickly become a curse for a compiler developer.  Simply discovering which test cases in a large set of failures represent distinct faults (and possibly already known faults) is a very difficult problem \cite{PLDI13,Podgurski04}.  For simple crashes and assertion violations, bucketing failures is sometimes easy.  When a failure is detected by differential testing \cite{Differential}, where two compilers or optimization levels disagree, the problem is so hard that it may turn potential users away from automated test generation \cite{PLDI13}.  Even once a fault is identified, fixing the problem can be very difficult.  There is reason to suspect, due to complexity of intermediate representation, interaction of a very large number of optimizations, subtle aspects of language semantics, and other issues, that debugging compiler faults may usually be harder than debugging faults in other kinds of software (this is probably not limited to compilers; debugging systems software in general is hard \cite{mickens}).
We propose the use of mutants \cite{mutant}, small syntactic changes to source code, to address some of the problems of debugging based on large sets of automatically generated test cases.  The underlying idea is that if two failures can be repaired in the same way, even if that repair only avoids the failure and does not truly fix it, they are likely due to the same fault. Repairs can also provide  information for understanding and debugging discovered faults. This approach also suggests a possible metric for comparing any two program executions, not just failing test cases.

>>>>

Recent advances in automated test generation, reported in numerous papers and implemented in powerful tools \cite{csmith,jsfunfuzz,ISSTA12,LangFuzz,ZhendongPLDI,ZhendongOOPSLA}, have made it easier to find subtle faults in, e.g., modern optimizing compilers\footnote{In this paper, we take the problem of testing and debugging compilers as representative of the general problem of testing and debugging complex critical systems software.}  Unfortunately, the blessing of many failing test cases can become a curse for a developer.  Simply discovering which test cases in a large set of failures represent distinct faults (or already known faults) is a very difficult problem \cite{PLDI13,Podgurski04}.  For simple crashes and assertion violations, bucketing failures is sometimes easy.  When a failure is detected by differential testing \cite{Differential}, where two compilers or optimization levels disagree, the problem is so hard that it may turn potential users away from automated test generation \cite{PLDI13}.  Even once a fault is identified, fixing the problem can be very difficult.  Due to complexity of intermediate representation, interaction of optimizations, subtle language semantics, and other issues, debugging compiler faults may often be harder than debugging faults in other kinds of software (this is probably not limited to compilers; debugging systems software in general is hard \cite{mickens}).
We propose the use of program mutants \cite{mutant} to assist debugging based on large sets of automatically generated test cases.  The underlying idea is that if two failures can be repaired in the same way, even if that repair only avoids the failure and does not truly fix it, they are likely due to the same fault. Repairs can also provide  information for understanding and debugging discovered faults. This approach also suggests a possible metric for comparing any two program executions, not just failing test cases.
